\begin{thebibliography}{9}

\bibitem{CorteseEtAl08}
	Cortese, P.F., Di Battista, G., Frati, F., Patrignani, M., Pizzonia, M.: C-planarity of cconnected clustered graphs. J. Graph Alg. Appl. 12(2), 225–262 (2008).

\bibitem{CornelsenWagner03}
	Cornelsen, S., Wagner, D.:. Completely connected clustered graphs. Journal of Discrete Algorithms, 4(2):313–323, 2006.

\bibitem{JelinekEtAl08}
	Jelínek, V., Jelínková, E., Kratochvíl, J., Lidický, B.: Clustered Planarity: Embedded Clustered Graphs with Two-Component Clusters (extended abstract), Proceedings of Graph Drawing 2008, LNCS 5417 (2009), 121-132.

\bibitem{GutwengerEtAl02}
	Gutwenger, C., Jünger, M., Leipert, S., Mutzel, P., Percan, M., Weiskircher, R.: Advances in c-planarity testing of clustered graphs. In: Goodrich, M.T., Kobourov, S.G. (eds.) GD’02. LNCS, vol. 2528, pp. 220–235. Springer (2002).

\bibitem{GoodrichEtAl05}
	Goodrich, M.T., Lueker, G.S., Sun, J.Z.: C-planarity of extrovert clustered graphs. In: Healy,P., Nikolov, N.S. (eds.) GD’05. LNCS, vol. 3843, pp. 211–222. Springer (2006).

\bibitem{JelinkovaEtAl07}
	Jelínková, E., Kára, J., Kratochvíl, J., Pergel, M., Suchý, O., Vyskočil, T.: Clustered planarity: Small clusters in cycles and eulerian graphs. J. Graph Alg. Appl. 13(3), 379–422 (2009).

\bibitem{CorteseEtAl04}
	Cortese, P. F., Di Battista, G., Patrignani, M., Pizzonia, M.: Clustering cycles into cycles of clusters. Journal of Graph Algorithms and Applications, 9(3):391–413, 2005.

\bibitem{CorteseEtAl09}
	Cortese, P. F., Di Battista, G., Patrignani, M., Pizzonia, M.: On embedding a cycle in a plane graph. In Proceedings of 13th International Symposium on Graph Drawing 2005, volume 3843 of LNCS, pages 49–60. Springer, Heidelberg, 2006.

\bibitem{DiBattistaFrati07}
	Di Battista, G., Frati, F.: Efficient c-planarity testing for embedded flat clustered graphs with small faces. In: Hong, S.H., Nishizeki, T., Quan, W. (eds.) GD’07. LNCS, vol. 4875, pp. 291–302. Springer (2008).

\bibitem{AngeliniEtAl10}
	Angelini, P., Di Battista, G., Frati, F., Jelínek, V., Kratochvíl, J., Patrignani, M., Rutter, I.: Testing Planarity of Partially Embedded Graphs, Proceedings of SODA 2010, 202-221.

\bibitem{JelinekEtAl10}
	Jelínek, V., Kratochvíl, J., Rutter, I.: A Kuratowski-Type Theorem for Planarity of Partially Embedded Graphs, Computational Geometry - Theory and Applications, 46(4) (2013), 466-492.

\bibitem{BiedlI98}
	Biedl, T.: Drawing planar partitions I; LL-drawings and LH-drawings. Technical Report RRR 11-98, RUTCOR, Rutgers University, 1998.

\bibitem{BiedlII98}
	 Bied, T., Kaufmannl, M., Mutzel, P.: Drawing planar partitions II: 
HH-drawings. Technical Report RRR 12-98, RUTCOR, Rutgers University, 1998.

\bibitem{BiedlIII98}
	Biedl, T.: Drawing planar partitions I; LL-drawings and LH-drawings. Technical Report RRR 11-98, RUTCOR, Rutgers University, 1998.

\bibitem{lca}
	Lowest common ancestor --- Wikipedia, The Free Encyclopedia, http://en.wikipedia.org/wiki/Lowest\_common\_ancestor, Online; accessed 16-May-2015.


\bibitem{rmq}
	Range minimum query --- Wikipedia, The Free Encyclopedia, http://en.wikipedia.org/wiki/Range\_minimum\_query, Online; accessed 16-May-2015.


\bibitem{savitch}
	Savitch's theorem --- Wikipedia, The Free Encyclopedia, http://en.wikipedia.org/wiki/Savitch's\_theorem, Online; accessed 16-May-2015.


\end{thebibliography}